|

### 2025-05-19 manuscript/paper.Rmd
added some citations.

 <!-- Non-Enforcer 0.8795039 0.8308666 0.9309884 75.01096 -->
 <!-- Enforcer 0.7448857 0.6142941 0.9032394 75.01096 -->

@@

@@

```
#total fights continuous and NA
```{r fig:estsurv:TF, echo = FALSE, fig.cap = "Estimated Survival curve for EF for defenders.  All other variables are fixed at their mean level (GP = 285.8, Ht = 72.7in, Wt = 197.03, and Year of birth 1974.5."}
#coxphmod_Total.Fights <- coxph(Surv ~ Total.Fights  + GP.x + Ht + Wt + DOB.Year + Pos2, data = dat)
coxphmod_Total.Fights <- coxph(Surv ~ Total.Fights + GP.x + Ht + Wt + DOB.Year + Pos2, data = dat)
#xtable(summary(coxphmod_Total.Fights)$coef[,-4],digits = 5)

>>>>

 <!-- Non-Enforcer 0.8795039 0.8308666 0.9309884 75.01096 -->
 <!-- Enforcer 0.7448857 0.6142941 0.9032394 75.01096 -->
ddd

@@

<!-- Englehardt, G. M. (1995). Fighting behavior and winning national hockey league games: A paradox. Perceptual and -->
<!-- Motor Skills, 80, 416–418. -->
<!-- Kirker, B., Tennenbaum, G., & Mattson, J. (2000). An investigation of the dynamics of aggression: Direct observation -->
<!-- in ice hockey and basketball. Research Quarterly for Exercise and Sport, 71, 373–386. -->
<!-- McCarthy, J. F., & Kelly, B. R. (1978a). Aggressive behavior and its effect on performance over time in ice hockey -->
<!-- athletes: An archival study. International Journal of Sport Psychology, 9, 90–96. -->
<!-- Wennberg, R. (2004). Collision frequency in elite hockey on North American versus International size rinks. Canadian -->
<!-- Journal of Neurological Sciences, 31, 373–377 -->

@@

```
#total fights continuous and NA

```{r fig:estsurv:TF, echo = FALSE, fig.cap = "Estimated Survival curve for EF for defenders.  All other variables are fixed at their mean level (GP = 285.8, Ht = 72.7in, Wt = 197.03, and Year of birth 1974.5."}
#coxphmod_Total.Fights <- coxph(Surv ~ Total.Fights  + GP.x + Ht + Wt + DOB.Year + Pos2, data = dat)
coxphmod_Total.Fights <- coxph(Surv ~ Total.Fights + GP.x + Ht + Wt + DOB.Year + Pos2, data = dat)
#xtable(summary(coxphmod_Total.Fights)$coef[,-4],digits = 5)
